\documentclass[11pt, a4paper]{article}
\pagestyle{empty}
\usepackage{amsfonts, amssymb, amsmath}
\usepackage{float,enumerate,hyperref}
\usepackage{tikz,pgfplots,graphicx}
\usepackage{xcolor,colortbl}
\usepackage{enumitem}
%\usepackage{fullpage}
\usepackage[top=1in,left=0.5in,right=0.5in,bottom=1in]{geometry}
\parindent 0px


\begin{document}

\noindent  \begin{flushright}\begin{Large}\textbf{Ankesh K.} \end{Large}\end{flushright}
\vspace{-2mm}
\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
GitHub: [\url{github.com/iankesh}] & DevOps Consultant \\
Blogs: [\url{blogspot.com/iankesh}] & Bengaluru, Karnataka – 37 \\
LinkedIn: [\url{linkedin.com/in/iankesh}] &  \href{mailto:iankesh@outlook.com}{iankesh@outlook.com} \\
Website: [\url{iankesh.wixsite.com/profile}] &  +91 819 743 4654\\
\hline
\end{tabular*}

\section*{Career Objective}
A DevOps evangelist with 4.6+ years of experience and working knowledge of DevOps, DevSecOps, Automation, CI/CD - Pipeline as Code,  Infrastructure as Code (IAC), Cloud Operations and Build \& Release Management. Hands-on experience in creating and automating deployments, leveraging configuration management and DevOps. Aiming to leverage my skills to successfully fill the DevOps role at your company.

\section*{Education}
\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
\textbf{AMC Engineering College} & Bengaluru, KA  \\
Bachelor of Engineering (B.E.) - VTU & 2011 - 2015
\end{tabular*}

\section*{Work Experience}
\noindent\begin{tabular*}{\textwidth}{|@{\extracolsep{\fill}}l r|}
\hline
\textbf{HACH (A Danaher Company)} & Bengaluru, KA  \\
Software Consultant - DevOps \& Sr.  Software Engineer - DevOps & Apr 2019 - Present \\
\hline
\textbf{Mindtree Ltd.} & Chennai,  TN \& Bengaluru, KA  \\
Sr. Engineer - DevOps \& Engineer - DevOps & Feb 2016 - Apr 2019 \\
\hline
\end{tabular*}
\vspace{1mm}
\begin{itemize}[noitemsep, nolistsep]
\item Having practical experience working with DevOps tools, SCM, Automation, CI/CD, Configuration Mgmt., Build \& Release Mgmt. and Cloud Operations.
\item Extensively working on Terraform and Ansible to create Infrastructure as Code (IAC) for the new environments, migrated all the legacy ones and maintaining the state of all the environments.
\item Followed best practices of Software Configuration Management (SCM) processes, which includes compiling, packaging, deploying and configurations.
\item Created a tool named D-Engine which is used for automated infra creation and orchestration.
\item Following, learning and implementing Danaher Business System (DBS).
\item Working on a dot-net multi-stack microservice architecture using Azure Service Fabrics to package, deploy, and manage scalable and reliable microservices and containers.
\item Working with DevFinOps approach for cloud and saving  approx.  $\$3,000,000/year$ with the analysis using Kusto Query Language – KQL, Log Analytics and Application Insights.
\item Single handedly managing and performing the complete Production releases with respective Development, QA and support teams, along with Rollback planning.
\item Automated manual processes at different levels of SDLC using different technologies and scripts.
\item Created a complete monitoring solution for an IOT product using Grafana and Nagios.
\item Extensively experienced in scripting languages like Shell on Linux and PowerShell on Windows.
\item Working with Containerization tools like Docker and Kubernetes to create dynamic Jenkins slaves.
\item Implementing DevSecOps as a part of DevOps pipeline using tools like SonarQube, Prisma, etc.
\item Implemented multiple CI (Continuous Integration), CD (Continuous Deployment) and CD (Continuous Delivery) pipelines as a part of DevOps role in multiple projects.
\item Have good understanding of Incident, Problem and Change management and ability to work independently or as part of a team.
\item Training and handling colleagues and juniors in the team and preparing High-level POCs.
\end{itemize}
\pagebreak

\section*{Professional Skills}
\noindent\begin{tabular}{|p{1.8in}|p{5.15in}|}
\hline
DevOps Skillset & Infrastructure as Code - IAC, Automation, CI/CD, Build \& Release Mgmt. \\
\hline
DevOps Stack & Java/Dot-Net Stack, HashiCorp Tools, Atlassian Tools \\
\hline
Operating System & MacOS, Windows, Ubuntu, CentOS, Red Hat, Kali Linux, Parrot OS \\
\hline
Continuous Integration & Jenkins, Bamboo, Azure DevOps (VSTS), TFS, TeamCity \\
\hline
Configuration Management 	& Terraform, Ansible, Jenkins Pipeline and Basics of Chef \\
\hline
Cloud Operations 	& Microsoft Azure, Amazon Web Services - AWS \\
\hline
Command Line Interface & AWS CLI, Azure CLI, Linux, Windows \\
\hline
Containerization  & Docker, Kubernetes, Azure Kubernetes Service – AKS, Azure Service Fabrics \\
\hline
DevSecOps/Security & Trufflehog, OWASP Top 10, Nikto, DefectDojo, Prisma Cloud \\
\hline
Version Control & Git, GitHub, GitLab, BitBucket \\
\hline
Build \& Repo Management  & Packer, Maven and JFrog Artifactory \\
\hline
Languages	 & Bash Shell, PowerShell, C++, KQL, Python \\
\hline
Web Tools/Technologies  & Apache Tomcat, Nginx, HA Proxy \\
\hline
Deployment & Jenkins – Pipeline as Code, Bamboo, Azure DevOps, Rundeck \\
\hline
Ticketing \& Management  & JIRA, Remedyforce \\
\hline
Monitoring \& Code Quality	 & Grafana, Nagios, SonarQube, Application Insights \\
\hline
Team Collaboration & MS Teams, Slack, Confluence \\
\hline
Human Skills & Communication, Decision Making, Leadership, Teamwork, Adaptability \\
\hline
Danaher Business System &	DBS Fundamentals, Problem Solving Practice (PSP)\\
\hline
%\multicolumn{2}{|c|}{\text{Title}} \\
%\hline
\end{tabular}

\section*{Roles - [Core Technical]}
	\subsection*{At HACH - A Danaher Company}
Working for the product-based firm named “HACH” which is a Danaher company.  Extensively working on a product called “Claros - The Water Intelligence System”. It is a digital IoT solution to eliminate uncertainty and improve efficiency. \\

\noindent\begin{tabular}{|p{1in}|p{5.95in}|}
\hline
\rowcolor{black!20} Role [4] & Software Consultant - DevOps\\
\hline
Duration & April 2020 - Present\\
\hline
Team Size & 5[70\%] \& Individual Contributor[30\%]\\
\hline
\end{tabular}
\newline
\vspace*{1mm}
\newline
\begin{tabular}{|p{7.122in}|}
\hline
\rowcolor{black!5} Responsibilities \& Tasks\\
\hline
\begin{itemize}[noitemsep, nolistsep]
\item First item
\item Second item
\item Third item
\item First item
\item Second item
\item Third item
\end{itemize} \\
\hline
\end{tabular}
\pagebreak

\noindent\begin{tabular}{|p{1in}|p{5.95in}|}
\hline
\rowcolor{black!20} Role [3] & Sr. Software Engineer - DevOps\\
\hline
Duration & April 2019 - April 2020\\
\hline
Team Size & 5[100\%]\\
\hline
\end{tabular}
\newline
\vspace*{1mm}
\newline
\begin{tabular}{|p{7.122in}|}
\hline
\rowcolor{black!5} Responsibilities \& Tasks\\
\hline
\begin{itemize}[noitemsep, nolistsep]
\item First item
\item Second item
\item Third item
\item First item
\item Second item
\item Third item
\end{itemize} \\
\hline
\end{tabular}

	\subsection*{At Mindtree Ltd.}



\end{document}
